\documentclass[12pt, titlepage]{article}

\usepackage{amsmath, mathtools}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{xspace}

\usepackage{graphicx}
\usepackage{colortbl}
\usepackage{xr}
\usepackage{longtable}
\usepackage{xfrac}
\usepackage{float}
\usepackage{siunitx}
\usepackage{caption}
\usepackage{pdflscape}
\usepackage{afterpage}

\usepackage{fullpage}
\usepackage[round]{natbib}
%\usepackage{refcheck}
\usepackage{lipsum}

\input{../Comments}
\input{../Common}

\newcounter{reqnum} %Requirement Number
\newcommand{\rthereqnum}{P\thereqnum}
\newcommand{\rref}[1]{R\ref{#1}}

\begin{document}

\title{System Verification and Validation Plan for \progname{L}:
software estimating the radius of convergence of a power series} 
\author{John M Ernsthausen}
\date{\today}
	
\maketitle

~\newpage

\pagenumbering{roman}

\tableofcontents

\listoftables

\listoffigures

~\newpage

\section*{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
\midrule
29 October 2020 & 1.0 & First submission\\
\bottomrule
\end{tabularx}

~\newpage

\section{Symbols, Abbreviations, and Acronyms}

Symbols, abbreviations, and acronyms applicable to \progname{f} are enumerated
in Section 1 of the Software Requirements Document (SRS) \citep{SRS}.

\newpage

\pagenumbering{arabic}

% \input examples
% \input lagrangianfacility
% \input mechfacility
% \input vec3d
% \input fcn 
% \printindex

%CHAPTER
\section{Introduction} \label{sc:introduction}

Construct the series centered at $z_0 \in \Rz$
\EQ
{
  \label{eq:power-series}
  \sum_{n=0}^{\infty} c_n (z-z_0)^n
}
from a sequence $\Setbg{c_n}$ of real numbers where the $n^\text{th}$ term in the sequence corresponds
to the $n^\text{th}$ coefficient in the series. We associate a sequence $\Setbg{s_n}$ of partial sums
\EQ
{
  \label{eq:partial-sum}
  s_n \defeq \sum_{k=0}^n c_k (z-z_0)^k
}
with the power series. If $\Setbg{s_n} \rightarrow s$ as $n \rightarrow \infty$,
then we say $\Setbg{s_n}$ converges to $s$. The number $s$ is the sum of the series, and
we write $s$ as \eqref{power-series}. If $\Setbg{s_n}$ diverges, then the series is said to diverge.

We cannot perform an infinite sum on a digital computer. However, given a tolerance \tol
and a convergent power series, there exists an integer $N$ such that, for all
$m \geq n \geq N$, $| \sum_{k=n}^{m} c_k | < \tol$. We assume that we know $N$. Our software
\progname{f} will estimate the radius of convergence $R_c$ from the first $N$ terms 
in the power series. The coefficients may be scaled with a scaling $h$ to
prevent numerical overflow. The default scaling is $h=1$. Scaling the coefficients
is a change of variables $v(z) \defeq (z - z_0)/h$ in \eqref{power-series}. With the scaled coefficients
 $\tilde c_n \defeq c_n h^n$ and the change of variables, \eqref{power-series} transforms to
\EQ
{
  \label{eq:power-series-scaled}
  \sum_{n=0}^{\infty} \tilde c_n v^n.
}
When $r_c$ is the radius of the circle of convergence of \eqref{power-series-scaled}, $R_c = h r_c$
is the radius of the circle of convergence of \eqref{power-series}.
\progname{f} may not compute $R_c$ exactly. These are the assumptions under which the \progname{f} software
operates. In the sequel, we denote both scaled and unscaled coefficients by $c_n$.

Corliss and Chang \cite{chang1982} (CC) observed that the coefficients of \eqref{power-series} follow a few
very definite patterns characterized by the location of primary singularities. Real valued power series
can only have poles, logarithmic branch points, and essential singularities. Moreover, these singularities
occur on the real axis or in complex conjugate pairs. The effects of secondary singularities disappear
whenever sufficiently long power series are used. To determine $R_c$ and the order of the singularity $\mu$,
CC fit a given finite sequence to a model.

Recall that a primary singularity of \eqref{power-series} is the closest singularity to the series
expansion point $z_0$ in the complex plane. All other singularities are secondary singularities.

This document provides a verification and validation plan for developing \progname{f}.

%CHAPTER
\section{General Information}

The scope of this \progname{f} project is limited to top-line analysis.
Top-line analysis always applies to any power series \eqref{power-series}. It resolves situations
where secondary singularities are less distinguishable from primary singularities. However it is
less accurate. It does have a convergence analysis \cite{chang1982}.

\subsection{Summary}

In \cite{SRS}, we detailed the algorithm implementing top-line analysis.

\paragraph{Module findrc} \label{findrc}
We know the tolerance $\tol$, the scale $h$, the integer $N$, and the sequence
$\Setbg{c_0, c_1, \ldots, c_{N}}$ by assumption, as in \SCref{introduction}.
We extract the last $15$ terms from the sequence.
With $k = i+N-14$, obtain the best linear fit $y(k) = m k + b$ in the $2$-norm to the points
\EQ
{
  \label{eq:approximation-points}
  \Setbg{(N-14, \log_{10} | c_{N-14} |), (N-13, \log_{10} |c_{N-13}|), \ldots, (N, \log_{10} |c_{N}|)},
}
that is, find $m$ and $b$ such that $\sum_{i=0}^{14} |\log_{10} |c_{i+N-14}| - y(i+N-14)|^2$ is minimized.
The approximation problem \eqref{approximation-points} is the well known
{\it linear least-squares problem} \cite{GoVL89}.
The model parameter $m$ will be negative whenever the series \eqref{power-series} converges and
positive whenever it diverges.The raidus of convergence $R_c = h/10^m$.

\paragraph{Module findmu}
Start with the series resulting from integration of the given series three times and
fit the coefficients with Module {\bf findrc}. If that graph is linear, meaning the
minimizer has norm less than \tol, then the slope is accepted and the order of the
singularity is 3. If the graph opens upward, then the series is differentiated term-wise
to reduce the second derivative of the graph, and a new top-line fit is computed with
Module {\bf findrc}. This process is repeated, reducing $\mu$ by 1 each time, until the
graph opens downward or until seven term-wise differentiations have been tested.
If seven term-wise differentiations have been tested and each result in turn proves
unsatisfactory, then the final estimate for $R_c$ is reduced by 10 percent for a
conservative estimate for $R_c$ and $\mu=-4$ is returned.

We implement Module {\bf findrc} and Module {\bf findrc} in \progname{f}.
This document provides plan for verification and validation \progname{f} while implementing
these modules in \cpp.

\subsection{Objectives}

Our objective it to implement Module {\bf findrc} and Module {\bf findrc} via
{\it test driving} in \cpp. The implementation must satisfy the requirements
enumerated in \cite{SRS}.

Assume that the assumptions are satisfied. Recall the requirements

\noindent \begin{itemize}

\item[R\refstepcounter{reqnum}\thereqnum \label{R_Inputs}:] The input
  sequence should be scaled by $h$ to prevent overflow/underflow.
  If this is not possible, \progname{f} will find a scale.

\item[R\refstepcounter{reqnum}\thereqnum \label{R_Calculate}:]
  \progname{f} should execute as fast as the CC software \rdcon.

\item[R\refstepcounter{reqnum}\thereqnum \label{R_VerifyOutput}:]
  \progname{f} should estimate the radius of convergence $R_c$ and
    the order of singularity $\mu$ for the following cases where $R_c$ and $\mu$ are known.

  The real valued function $1/(z-z_0)^{\mu}$.

  The real valued function $1/(1 + 25*(z-z_0)^2)^{\mu}$.

  Top line analysis while solving \dae \ivp by the TS method should verify
    the computed step is within the circle of convergence and compare
    with the CC algorithm \rdcon.

\item[R\refstepcounter{reqnum}\thereqnum \label{R_Output}:] We must not overestimate $R_c$.
  If $R_c$ is overestimated, then the power-series is a divergence sum on the overestimation.

  In \ode solving by TS methods, underestimating $R_c$ is acceptable as an underestimation
  results in a slight increase in computational effort for solving an \ode \ivp.
\end{itemize}

In a nutshell these requirements validate and verify \progname{f}.

\subsection{Relevant Documentation}

Relevant documentation includes the authors Software Requirements (SRS) Document \cite{SRS}, the
authors Module Guide (MG, to be written), and the authors Module Interface Specification (MIS, to be written).

\section{Verification and Validation Plan}

Verification and Validation of \progname{f} includes automated testing at the module level,
the system level, and integration level. This document will additionally propose continuous integration.

\subsection{Verification and Validation Team}

The \progname{f} team includes
author
\href{https://github.com/JohnErnsthausen}{John Ernsthausen},
fellow students
\href{https://github.com/LeilaMousapour}{Leila Mousapour},
\href{https://github.com/salahhessien}{Salah Gamal aly Hessien},
\href{https://github.com/liziscool}{Liz Hofer},
and
\href{https://github.com/XingzhiMac}{Xingzhi Liu} as well as Professors
\href{http://baraksh.com}{Barak Shoshany},
\href{https://github.com/smiths}{Spencer Smith},
\href{https://www.cs.mu.edu/~george/}{George Corliss},
and
\href{http://www.cas.mcmaster.ca/~nedialk}{Ned Nedialkov}.
The author appreciates the helpful comments and superior guidance on this project.

\subsection{SRS Verification Plan}

The SRS document Verification and Validation Plan for \progname{f} will be peer-reviewed by
domain expert Leila Mousapour and secondary reviewer Salah Gamal aly Hessien.
Prof. Spencer Smith the course instructor and my supervisor Ned Nedialkov will review the SRS
document.

The SRS document will be published to \href{https://github.com/JohnErnsthausen/roc}{GitHub}.
Defects will be addressed with issues on the GitHub platform.

\subsection{Design Verification Plan}

The Design documents MG and MIS plan for \progname{f} will be peer-reviewed by
domain expert Leila Mousapour and secondary reviewer Xingzhi Liu.
Prof. Spencer Smith the course instructor and my supervisor Ned Nedialkov will also review these Design
documents.

The MG and MIS documents will be published to \href{https://github.com/JohnErnsthausen/roc}{GitHub}.
Defects will be addressed with issues on the GitHub platform.

\subsection{Implementation Verification Plan}

The Implementation Verification Plan for \progname{f} includes automated testing at the module level.
For testing at the module level, the author plans to follow the Test Driven Development
software development practices as described by \cite{langr2013} for {\it test driving}.
Test driving is an interactive process for software development where tests are determined
as part of the software development process. However on a high level, some unit tests
will be offered in the sequel.

Let us recall test driving \cite{langr2013}.
Test driving results in unit tests. A unit test verifies the {\it behavior} of a code unit,
where a {\it unit} is the smallest testable piece of an application.

A single unit test consists of a descriptive name and a series of code statements conceptually
divided into four parts

\begin{enumerate}
  \item (Optional) statements that set up a context for execution
  \item One or more statements to invoke the behavior to be verified
  \item One or more statements to verify the expected outcome
  \item (Optional) cleanup statements
\end{enumerate}

The first three parts are referred to as {\it Given-When-Then}. {\it Given} a context, {\it When}
the test executes some code, {\it Then} some behavior is verified.

Test Driven Development is used to test drive new behavior into the code in small increments. To
add a new piece of behavior into the system, first write a test to define that behavior. The
existence of a test that will not pass drives the developer to implement the corresponding behavior.
The increment should be the smallest meaningful amount of code, one or two lines of code and one assertion.

The code should be well formatted and free of memory leaks.

\subsection{Automated Testing and Verification Tools}

Automated Testing and Verification Tools will be extensively used in the development of \progname{f}
for automation at the module level, the system level, and integration level.
These tools include
\href{https://git.kernel.org/pub/scm/git/git.git}{git} a distributed version-control system
for tracking changes in source code during software development,
\href{https://cmake.org/}{cmake} for build automation,
\href{https://github.com/google/googletest}{gtest}
as a unit testing framework, \href{http://clang.llvm.org/docs/ClangFormat.html}{clang-format}
for consistent code style formatting, and \href{https://www.valgrind.org}{valgrind}
to identify memory leaks.

This document will additionally propose to branch out into three new areas for the author.
In the DevOps arena,
continuous integration will be persued with \href{https://travis-ci.org}{TravisCI}.
The continuous integration tool should send an email confirming the success state
of integrating the new code into production.
The author will explore the application of linters and metrics for code coverage.

\subsection{Software Validation Plan}

The Software Validation Plan for \progname{f} includes automated testing at the system level
and integration level. The code must validate known cases at the system level. The code output
will be compared with the output of \rdcon developed by CC for validation at the integration level.

\section{System Test Description}

System tests are about the public interface. Nonfunctional tests are removed from the
discussion because \progname{f} has no nonfunctional requirements at this time.
	
\subsection{Tests for Functional Requirements}

Functional requirements at the system level reflect \rref{R_Calculate} and
\rref{R_VerifyOutput}.

\subsubsection{Timing}

Requirement \rref{R_Calculate} says that \progname{f} should execute as fast as
the CC software \rdcon. The following tests represent a comparison between
\progname{f} and \rdcon.

\paragraph{Proportion of time spent finding the stepsize}

\begin{enumerate}

\item{Layne-Watson\\}

% Control: 
					
% Initial State: 
					
Input: Load a file with the Taylor series solution of the Layne-Watson problem. Each time the
    local initial value problem was solved there will be a Taylor series of length $N$ and a scale $h$,
    which are the required inputs for \progname{f} and \rdcon.
					
Output: Difference between time for \progname{f} to solve problem and time for \rdcon to solve problem.

Test Case Derivation: Two techniques resolving the same data.
					
How test will be performed: Automatically.
					
\item{Planetary-Motion\\}

% Control: 
					
% Initial State: 
					
Input: Load a file with the Taylor series solution of the Planetary-Motion problem. Each time the
    local initial value problem was solved there will be a Taylor series of length $N$ and a scale $h$,
    which are the required inputs for \progname{f} and \rdcon.
					
Output: Difference between time for \progname{f} to solve problem and time for \rdcon to solve problem.

Test Case Derivation: Two techniques resolving the same data.
					
How test will be performed: Automatically.

\end{enumerate}

\subsubsection{Accuracy}

Requirement \rref{R_VerifyOutput} says that the new top line
analysis in \progname{f} should compute a $R_c$ and $\mu$ which is
close to the values computed with the CC algorithm \rdcon.
This test treats \rdcon as a pseudo oracle.
The comparison will be carried out on the process of solving a \dae \ivp by the TS method.

\paragraph{Accuracy in finding the stepsize}

\begin{enumerate}

\item{Layne-Watson\\}

% Control: 
					
% Initial State: 
					
Input: Load a file with the Taylor series solution of the Layne-Watson problem. Each time the
    local initial value problem was solved there will be a Taylor series of length $N$ and a scale $h$,
    which are the required inputs for \progname{f} and \rdcon.
					
Output: Each time the local initial value problem was solved, find $R_c$ and $\mu$ with
    \progname{f} and \rdcon. Compare the results. Expect the results to compare within 10\%.

Test Case Derivation: Two techniques resolving the same data.
					
How test will be performed: Automatically.
					
\item{Planetary-Motion\\}

% Control: 
					
% Initial State: 
					
Input: Load a file with the Taylor series solution of the Planetary-Motion problem. Each time the
    local initial value problem was solved there will be a Taylor series of length $N$ and a scale $h$,
    which are the required inputs for \progname{f} and \rdcon.
					
Output: Each time the local initial value problem was solved, find $R_c$ and $\mu$ with
    \progname{f} and \rdcon. Compare the results. Expect the results to compare within 10\%.

Test Case Derivation: Two techniques resolving the same data.
					
How test will be performed: Automatically.

\end{enumerate}

% \subsection{Tests for Nonfunctional Requirements}
% 
% \wss{The nonfunctional requirements for accuracy will likely just reference the
%   appropriate functional tests from above.  The test cases should mention
%   reporting the relative error for these tests.}
% 
% \wss{Tests related to usability could include conducting a usability test and
%   survey.}
% 
% \subsubsection{Area of Testing1}
% 		
% \paragraph{Title for Test}
% 
% \begin{enumerate}
% 
% \item{test-id1\\}
% 
% Type: 
% 					
% Initial State: 
% 					
% Input/Condition: 
% 					
% Output/Result: 
% 					
% How test will be performed: 
% 					
% \item{test-id2\\}
% 
% Type: Functional, Dynamic, Manual, Static etc.
% 					
% Initial State: 
% 					
% Input: 
% 					
% Output: 
% 					
% How test will be performed: 
% 
% \end{enumerate}
% 
% \subsubsection{Area of Testing2}
% 
% ...

\subsection{Traceability Between Test Cases and Requirements}

In each test, the requirement supported by the test case is stated.

\section{Unit Test Description}

\wss{Reference your MIS and explain your overall philosophy for test case
  selection.}  
\wss{This section should not be filled in until after the MIS has
  been completed.}




%  \item[R\refstepcounter{reqnum}\thereqnum \label{R_Inputs}:] The input
%    sequence should be scaled by $h$ to prevent overflow/underflow.
%    If this is not possible, \progname{f} will find a scale.
%  
%  \item[R\refstepcounter{reqnum}\thereqnum \label{R_Calculate}:]
%    \progname{f} should execute as fast as the CC software \rdcon.
%  
%  \item[R\refstepcounter{reqnum}\thereqnum \label{R_VerifyOutput}:]
%    \progname{f} should estimate the radius of convergence $R_c$ and
%      the order of singularity $\mu$ for the following cases where $R_c$ and $\mu$ are known.
%  
%    The real valued function $1/(z-z_0)^{\mu}$.
%  
%    The real valued function $1/(1 + 25*(z-z_0)^2)^{\mu}$.
%  
%    Top line analysis while solving \dae \ivp by the TS method should verify
%      the computed step is within the circle of convergence and compare
%      with the CC algorithm \rdcon.
%  
%  \item[R\refstepcounter{reqnum}\thereqnum \label{R_Output}:] We must not overestimate $R_c$.
%    If $R_c$ is overestimated, then the power-series is a divergence sum on the overestimation.
%  
%    In \ode solving by TS methods, underestimating $R_c$ is acceptable as an underestimation
%    results in a slight increase in computational effort for solving an \ode \ivp.
%  \end{itemize}
\subsection{Unit Testing Scope}

\wss{What modules are outside of the scope.  If there are modules that are
  developed by someone else, then you would say here if you aren't planning on
  verifying them.  There may also be modules that are part of your software, but
  have a lower priority for verification than others.  If this is the case,
  explain your rationale for the ranking of module importance.}

\subsection{Tests for Functional Requirements}

\wss{Most of the verification will be through automated unit testing.  If
  appropriate specific modules can be verified by a non-testing based
  technique.  That can also be documented in this section.}

\subsubsection{Module 1}

\wss{Include a blurb here to explain why the subsections below cover the module.
  References to the MIS would be good.  You will want tests from a black box
  perspective and from a white box perspective.  Explain to the reader how the
  tests were selected.}

\begin{enumerate}

\item{test-id1\\}

Type: \wss{Functional, Dynamic, Manual, Automatic, Static etc. Most will
  be automatic}
					
Initial State: 
					
Input: 
					
Output: \wss{The expected result for the given inputs}

Test Case Derivation: \wss{Justify the expected value given in the Output field}

How test will be performed: 
					
\item{test-id2\\}

Type: \wss{Functional, Dynamic, Manual, Automatic, Static etc. Most will
  be automatic}
					
Initial State: 
					
Input: 
					
Output: \wss{The expected result for the given inputs}

Test Case Derivation: \wss{Justify the expected value given in the Output field}

How test will be performed: 

\item{...\\}
    
\end{enumerate}

\subsubsection{Module 2}

...

\subsection{Tests for Nonfunctional Requirements}

\wss{If there is a module that needs to be independently assessed for
  performance, those test cases can go here.  In some projects, planning for
  nonfunctional tests of units will not be that relevant.}

\wss{These tests may involve collecting performance data from previously
  mentioned functional tests.}

\subsubsection{Module ?}
		
\begin{enumerate}

\item{test-id1\\}

Type: \wss{Functional, Dynamic, Manual, Automatic, Static etc. Most will
  be automatic}
					
Initial State: 
					
Input/Condition: 
					
Output/Result: 
					
How test will be performed: 
					
\item{test-id2\\}

Type: Functional, Dynamic, Manual, Static etc.
					
Initial State: 
					
Input: 
					
Output: 
					
How test will be performed: 

\end{enumerate}

\subsubsection{Module ?}

...

\subsection{Traceability Between Test Cases and Modules}

\wss{Provide evidence that all of the modules have been considered.}
				
\bibliographystyle{plainnat}

\bibliography{../../refs/References}

%  \newpage
%  
%  \section{Appendix}
%  
%  This is where you can place additional information.
%  
%  \subsection{Symbolic Parameters}
%  
%  The definition of the test cases will call for SYMBOLIC\_CONSTANTS.
%  Their values are defined in this section for easy maintenance.
%  
%  \subsection{Usability Survey Questions?}
%  
%  \wss{This is a section that would be appropriate for some projects.}

\end{document}
